\documentclass[11pt]{article}
\usepackage{rotating}
\usepackage{graphicx}
\usepackage{booktabs} 
\usepackage{longtable}
\usepackage{changepage}
\usepackage[margin=1in]{geometry}  % nice margins
\usepackage{setspace}              % control line spacing
\usepackage{hyperref}              % nicer links
\setlength{\parindent}{0pt}        % no paragraph indent
\setlength{\parskip}{0.75em}       % space between paragraphs
\usepackage[margin=1in]{geometry}


% Will declare authors below
\title{Machine Learning Project Proposal}
\date{}

\begin{document}

\maketitle

\section{Team Information}

	\hspace*{\parindent}\textbf{All members:}  Archi Mehta, Kareena Raghubans, Ramyanaga Nagarur, 
Vasupradha Ramji, Sparsh Pandey

	\textbf{Project Coordinator:} Sparsh Pandey
	

\section{Dataset Selected}

\hspace*{\parindent}We will use the  \textbf{Covertype} dataset. This dataset can be found in UC Irvine's dataset repository. It contains 581,012 instances, 54 features, and 7 labels. Here is a link to the dataset: https://archive.ics.uci.edu/dataset/31/covertype \\

This dataset does NOT contain images. Instead, each instance describes a 30 x 30 meter cell with different feature such as elevation, soil type, etc. The labels are the specific type of tree each instance describes (such as Spruce, Cottonwood, Aspen, etc). 

\section{Basic Statistics of the Dataset}

The table below presents the descriptive statistics for all 55 features in the Forest CoverType dataset. For each feature, the table reports the number of observations, mean, standard deviation, minimum value, key quartiles (25, 50, and 75), as well as the maximum observed value. These summaries show the wide variation in terrain-related features such as elevation, slope, hydrology distances, and hillshade indices, as well as the sparsity of many binary wilderness and soil-type indicators. Together, these statistics provide an overview of the distribution and scale of each variable.

The creator of the dataset also states that out of the 4 areas sampled, area 2, Neota, had a greater mean elevation compared to areas 1 and 3, Rawah and Comanche Peak respectively. Area 4, Cache la Poudre, had the lowest mean elevation.

Each area also has a majority population. Neota is more likely to have spruce/fir, Rawah and Comanche Park have more lodgepole pine, spruce/fir, and aspen (in that order from highest to lowest). Finally, Cache la Poudre contains Ponderosa pine, Douglas-fir, and cottonwood/willow

\pagebreak

{\small
\input{table_basic_stats_all.tex}
}

\section{Methods to Implement}

\begin{itemize}
	\item Decision Tree: Ramyanaga Nagarur 
	\item Naive Bayes Classifier: Vasupradha Ramji
	\item Logistic Regression: Kareena Raghubans
	\item Linear Support Vector Machine: Archi Mehta
	\item Kernel Support Vector Machine: Sparsh Pandey
	\item Multi-layer Perceptrons: Ramyanaga Nagarur 
	\item Convolutional Neural Networks (CNN): Vasupradha Ramji
	\item Long Short-Term Memory Networks (LSTM): Archi Mehta
	\item Transformers: Sparsh Pandey
	\item Large Language Models (Decoder-only): Kareena Raghubans

\end{itemize}
\section{Evaluation}

For evaluation, we will use the following:

\begin{itemize}
	\item test, train, val accuracy
	\item precision and recall
	\item f1-score
	\item ROC and AUC curves
	\item t-score
	\item Odd ratio
\end{itemize}

\section{Timeline}

\begin{itemize}
	\item \textbf{March 6th:}

Get done with all traditional model and tune hyperparamters. Eval as we go, so all eval is done

Working on deep learning models. Either already coded, training, or a good plan is laid out to code it (depending on model)

	\item \textbf{April 10th:}

Finish all deep learning models and training (depending on model). Eval as well. Double check all trad model results.

\item \textbf{April 20th:}

Finalize report and presentation 

\item \textbf{April 27th:}

Pass over report and presentation with everyone to make final adjustments, and submit. 

\item \textbf{May 4th:}

This week is an extra week we kept in case any of this does not go according to plan. We have a week to adjust (which we hopefully should not need).

\end{itemize}

\end{document}